Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2016-11-13 documents/BrazilSlides/slides.tex
More progress, slides to present found inequalities

\documentclass[
    % hyperref={bookmarks=false,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
    xcolor={dvipsnames},
]{beamer}

@@

\title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
\author[Fraser]{T.C.~Fraser\inst{1}}
\institute[PI]
{
    \inst{1}%
    Perimeter Institute for Theoretical Physics\\
    Ontario, Canada
}
\date[QN 2016]{Quantum Networks, 2016}

@@

\begin{frame}
    \frametitle{Deriving Inequalities}
    Two necessary components to compatibility:
    \begin{enumerate}
        \item[1.] \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
        \begin{itemize}
            \item Is the marginal model contextual or non-contextual?
            \item 3 distinct ways to tackle this problem
            \begin{enumerate}
                \item[1.] Convex hull, Polytope projection, Fourier-Motzkin
                \item[2.] Possibilistic Hardy Inequalities (Hypergraph transversals)
                \item[3.] Linear Program Feasibility/Infeasibility
            \end{enumerate}
        \end{itemize}
    \end{enumerate}
    \begin{enumerate}
        \item[2.] \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
        \begin{itemize}
            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
        \end{itemize}
    \end{enumerate}
\end{frame}

@@

\begin{frame}
    \frametitle{Inflations of the Triangle Scenario}
    \begin{center}
    \begin{tabular}{cc}
        %\hline
        \scalebox{0.5}{\input{../../figures/causal_structures/triangle_scenario}}
        &
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral}}
        \\
        %\hline
        The Triangle Scenario
        &
        Spiral Inflation \\
        %\hline
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut}}
        &
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
        \\
        %\hline
        Cut Inflation
        &
        Large Inflation \\
        %\hline
    \end{tabular}
    \end{center}
\end{frame}

@@

\begin{frame}
    \frametitle{$d$-Separation Polynomial}

\begin{frame}
    \frametitle{Triangle Scenario}
    \begin{columns}
        \column{0.4\linewidth}
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
        \column{0.6\linewidth}
            \begin{itemize}
                \item Three parties $\nodes_O = \bc{A, B, C}$
                \item Pair-wise sharing three latent variables $\nodes_L = \bc{X, Y, Z}$
                \item \todo[TC]{Inject info about existing work}
                \item There exists \textit{quantum-accessible} distributions $\prob[ABC]$ that are \textit{incompatible} with the triangle scenario
            \end{itemize}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Fritz Distribution}
    The \term{Fritz Distribution $\prob[F]$}:
    \begin{itemize}
        \item three-party $\prob[F] = \prob[ABC]$
        \item each party has four outcomes
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Inflation Pipeline}
    \note[item]{Walk through how the inflation pipeline works}
\end{frame}

\begin{frame}
    \frametitle{Outcomes and Events}
    \begin{itemize}
        \item Set of \term{outcomes} $O_v$ for each variable $v$
        \item Set of \term{events} for a set of variables $V$
        \[ \Events{V} \defined \bc{s: V \to O_V \mid \forall v \in V, s\br{v} \in O_v} \]
    \end{itemize}
    \begin{definition}
        The set of events over the joint variables $\Events{\jointvar}$ are termed the \term{joint events}.
    \end{definition}
    \begin{definition}
        The set of events over the marginal contexts are the \term{marginal events}
        \[ \Events{\mscenario} \defined \coprod_{V \in \mscenario} \Events{V} \]
    \end{definition}
\end{frame}

\begin{frame}
    \frametitle{Distribution Vectors}
    \begin{itemize}
        \item \term{Joint Distribution Vector $\probvec^{\jointvar}$}
        \[ \forall j \in \Events{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
        \item \term{Marginal Distribution Vector $\probvec^{\mscenario}$}
        \[ \forall m \in \Events{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Incidence Matrix}
    \begin{itemize}
        \item Marginal Problem as linear program
        \begin{align*}
            \probvec^{\mscenario}_m &= {\sum}_{j} M_{m,j} \probvec^{\jointvar}_j \\
            \probvec^{\mscenario} &= M \tcdot \probvec^{\jointvar}
        \end{align*}
        \item \term{Incidence matrix} $M$ is a bit-wise matrix
        \item Row-indexed by marginal events $m \in \Events{\mscenario}$
        \item Column-indexed by joint events $j \in \Events{\jointvar}$
        \[ M_{m,j} = \begin{cases}
            1 & m = j|_{\Dom{m}} \\
            0 & \text{otherwise}
        \end{cases} \]
        \begin{gather*}
        \# \text{Columns} = \abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{O_{v}} \\
        \# \text{Rows} = \abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \prod_{v \in V} \abs{O_{v}}
        \end{gather*}

@@

\begin{frame}
    \frametitle{Application to Large Inflation}
    \begin{columns}
        \column{0.6\linewidth}
            \begin{itemize}
                \item Find compatibility inequalities for TS by finding non-contextuality inequalities for Large Inflation
                \item Marginal Scenario is the set of maximal pre-injectable sets
                \item 12 maximal pre-injectable sets (to follow)
            \end{itemize}
        \column{0.4\linewidth}
            \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Large Inflation Incidence}
    \begin{itemize}
        \item Joint variables are all of the observable nodes $\nodes_O' = \jointvar$
        \[ \jointvar = \bc{A_1, A_2, A_3, A_4,B_1, B_2, B_3, B_4,C_1, C_2, C_3, C_4} \]
        \item Marginal scenario is composed of pre-injectable sets $\mscenario = \PreInj[\graph]{\graph'}$
        \item Inequalities Violated by Fritz distribution are inherently $4$-outcome
        \item Incidence matrix $M$ is very large $\sim 2.25 \textsf{Gb}$
        \[ \# \text{Columns} = 4^{12} = 16,777,216 \]
        \[ \# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896 \]
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Inequalities Found}
\end{frame}

\section{Symmetries}
\begin{frame}
    \frametitle{Causal Symmetry}
    \begin{itemize}
        \item Desirable to find compatibility inequality $I$ such that
        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
        \item Compatibility is independent of variable labels
        \[ \forall \varphi \in \Perm{\nodes} : I \stackrel{\text{com}}{\rightarrow} \graph \implies \varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \varphi\bs{\graph}  \]
        \item If $\varphi\bs{\graph} = \graph$ then $\varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \graph$
    \end{itemize}
    \begin{definition}
        The \term{causal symmetry group} of causal structure $\graph$:
        \[ \Aut{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\bs{\graph} = \graph} \]
        Strictly speaking, one needs to preserve observable nodes:
        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Aut{\graph} \mid \varphi\bs{\nodes_O} = \nodes_O} \]
    \end{definition}
    \note<1>[item]{Fritz distribution is incompatible with Triangle scenario because party $C$ plays the role of measurement settings for both $A$ and $B$}
    \note<1>[item]{In order to find quantum distributions different from $P_F$ in the Triangle Scenario, it is therefore desirable to find a proof of its incompatibility (i.e. inequality) that is symmetric under exchange of parties}
    \note<1>[item]{Surprisingly, it is possible to do so!}
    \note<1>[item]{Here is how.}
    \note<1>[item]{First, we will formally define the symmetry group in question}
    \note<1>[item]{Causal symmetry group is the }
\end{frame}

@@

\begin{frame}
    \frametitle{Symmetric Inequalities}
\end{frame}

@@

\begin{frame}
    \frametitle{Parameterizing Unitary Group}
    \begin{itemize}
        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} demonstrate a parameterization of $\s{U}\br{d}$ where the parameters are organized in a $d \times d$-matrix of real values $\la_{n,m}$
        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n} RP_{n,m}}} \tcdot \bs{\prod_{l=1}^{d} GP_{l}} \]
        \item Global Phase Terms: $GP_{l} = \exp\br{iP_l \lambda_{l,l}}$
        \item Relative Phase Terms: $RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$
        \item Rotation Terms: $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
        \item Projection Operators: $P_l = \ket{l}\bra{l}$
        \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Network Permutation Matrix}
    \begin{columns}
        \column{0.6\linewidth}
        \begin{itemize}
            \item States and measurements in the Triangle Scenario are not aligned
            \item Without $\netperm$, $\prob[ABC]$ would be separable
            \item Required to align $B$'s measurement over $\Tr_{A,C}\br{\rho_{AB} \otimes \rho_{BC}}$
            \item $\netperm$ is a $2^6 \times 2^6$ matrix
        \end{itemize}
        \column{0.4\linewidth}
            \includegraphics[trim={1.0cm 1.2cm 1.0cm 1cm},clip,width=1.0\textwidth]{../../figures/perm_mtrx.pdf}
    \end{columns}
    \begin{itemize}
        \item Shifts one qubit to the left
        \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
    \end{itemize}

@@

\begin{frame}
    \frametitle{Non-Trivial Inequalities For Large Inflation}
\end{frame}

\begin{frame}
    \frametitle{Conclusions}
\end{frame}

>>>>

\documentclass[
    hyperref={bookmarks=false,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
    xcolor={dvipsnames},
]{beamer}

\usetheme[height=8mm]{Rochester}
\usecolortheme{default}

@@

\title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
\author[Fraser]{T.C.~Fraser\inst{1}}
\institute[PI]
{
    \inst{1}%
    Perimeter Institute for Theoretical Physics\\
    Ontario, Canada
}
\date[QN 2016]{Quantum Networks IIP, Nov. 2016}

@@

\begin{frame}
    \frametitle{Deriving Inequalities}
    Two necessary components to compatibility:
    \begin{enumerate}
        \item \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
        \begin{itemize}
            \item Is the marginal model contextual or non-contextual?
            \item 3 distinct ways to tackle this problem
            \begin{enumerate}
                \item Convex hull, Polytope projection, Fourier-Motzkin
                \item Possibilistic Hardy Inequalities (Hypergraph transversals)
                \item Linear Program Feasibility/Infeasibility
            \end{enumerate}
        \end{itemize}
        \item \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
        \begin{itemize}
            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
        \end{itemize}
    \end{enumerate}
\end{frame}

@@

\begin{frame}
    \frametitle{Some Inflations of the Triangle Scenario}
    \begin{center}
    \begin{tabular}{cc}
        %\hline
        \scalebox{0.5}{\input{../../figures/causal_structures/triangle_scenario}}
        &
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral}}
        \\
        %\hline
        The Triangle Scenario
        &
        Spiral Inflation \\
        %\hline
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut}}
        &
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
        \\
        %\hline
        Cut Inflation
        &
        Large Inflation \\
        %\hline
    \end{tabular}
    \end{center}
\end{frame}

@@

\begin{frame}
    \frametitle{$d$-Separation Polynomial}
    \begin{itemize}
        \item Deflation only holds when inequality constrains probabilities $\prob[N'], N' \in \Inj[\graph]{\graph'}$
        \item \textbf{Linear inequality} for $\graph'$
    \end{itemize}
    \begin{center}
        \begin{tikzpicture}[scale=0.8]
            \pgfmathsetmacro{\hs}{1.8};
            \pgfmathsetmacro{\vs}{1};
            \pgfmathsetmacro{\cross}{0.3};
            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
            \draw (2*\hs, 4*\vs + 0.5*\vs) node[]{$N_1' \cup N_2' = N$};
            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
            \draw (0, 0) node[](b){??};
            \draw[thick, ] (a) -- (ab);
            \draw[thick, ] (c) -- (cd);
            \draw[thick, ] (a) -- (ac);
            \draw[thick, ->] (ac) -- (c);
            \draw[thick, ->] (ab) -- (b);
            \draw[thick, ->] (cd) -- (d);
            \draw[very thick, red]
            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
            ;
        \end{tikzpicture}
    \end{center}
    \begin{itemize}
        \item \textbf{Polynomial inequality} for $\graph$!
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Pre-injectable Sets}
    \begin{itemize}
        \item $d$-separation relations $+$ inflation $=$ polynomial inequalities over $\graph$
        \item Restrict focus to sets $N'$ that are partitioned into $N_1', N_2'$ $d$-separated by empty set $\emptyset$
        \item A \term{pre-injectable set} $N'$:
        \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
        \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
        \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Pre-injectable Sets of Large Inflation}
    \begin{center}
        \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
    \end{center}
    \begin{itemize}
        \item Has $12$ maximal pre-injectable sets (to follow)
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Deriving Inequalities}
    \begin{itemize}
        \item Inflation facilitates turning linear, inflated inequalities into polynomial deflated ones
        \item \textbf{Question:} How to derive compatibility inequalities for $\graph'$?
        \item \textbf{Answer:} Use your favorite technique for deriving compatibility inequalities:
        \begin{itemize}
            \item Entropic inequalities
            \item Finite outcome inequalities
        \end{itemize}
        \item Here we solve the marginal problem for $\mscenario = \PreInj[\graph]{\graph'}$
        \item First some notation and formalism
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Outcomes and Events}
    \begin{definition}
        Each variable $v$ has finite set of \term{outcomes} $O_v$. \\
        Each set of variables $V$ has finite set of \term{events} $\Events{V}$:
        \[ \Events{V} \defined \bc{s: V \to O_V \mid \forall v \in V, s\br{v} \in O_v} \]
    \end{definition}
    \begin{definition}
        The set of events over the joint variables $\Events{\jointvar}$ are termed the \term{joint events}.
    \end{definition}
    \begin{definition}
        The set of events over the marginal contexts are the \term{marginal events}
        \[ \Events{\mscenario} \defined \coprod_{V \in \mscenario} \Events{V} \]
    \end{definition}
\end{frame}

\begin{frame}
    \frametitle{Distribution Vectors}
    \begin{definition}
        The \term{joint distribution vector} $\probvec^{\jointvar}$
        \[ \probvec^{\jointvar}_j = \prob[\jointvar][j] \quad \forall j \in \Events{\jointvar}\]
    \end{definition}
    \begin{definition}
        The \term{marginal distribution vector} $\probvec^{\mscenario}$
        \[ \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \quad \forall m \in \Events{\mscenario}, \Dom{m} \in \mscenario\]
    \end{definition}
    Can now write complete marginal problem as matrix multiplication:
    \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \iff \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \]
\end{frame}

\begin{frame}
    \frametitle{Incidence Matrix}
    \begin{itemize}
        \item \term{Incidence matrix} $M$ is a bit-wise matrix
        \item Row-indexed by marginal events $m \in \Events{\mscenario}$
        \item Column-indexed by joint events $j \in \Events{\jointvar}$
        \[ M_{m,j} = \begin{cases}
            1 & m = j|_{\Dom{m}} \\
            0 & \text{otherwise}
        \end{cases} \]
        \begin{gather*}
        \# \text{Columns} = \abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{O_{v}} \\
        \# \text{Rows} = \abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \prod_{v \in V} \abs{O_{v}}
        \end{gather*}

@@

\begin{frame}
    \frametitle{Marginal Linear Program}
    \begin{itemize}
        \item Obtain inequalities from incidence matrix $M$ and known incompatible distribution $\probvec^{\mscenario}$
    \end{itemize}
    \begin{columns}[T]
        \column{0.4\linewidth}%
            \term{Marginal LP}:%
            \begin{alignat*}{2}
                & \text{minimize:} \quad&& \emptyset \tcdot x\\
                & \text{subject to:} && x \succeq 0 \\
                & && M \tcdot x = \probvec^{\mscenario} \\
            \end{alignat*}%
        \column{0.4\linewidth}%
            \term{Dual Marginal LP}:%
            \begin{alignat*}{2}
                & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
                & \text{subject to:} && y \tcdot M \succeq 0 \\
            \end{alignat*}%
    \end{columns}
    \begin{itemize}
        \item $y$ is an \term{infeasibility certificate}:
        \[ y \tcdot M \tcdot x = y \tcdot \probvec^{\mscenario} \geq 0  \]
        \item \term{Infeasibility inequality}: $y \tcdot \probvec^{\mscenario} \geq 0$
        \item Most linear programing toolkits return certificates (\href[pdfnewwindow]{http://docs.mosek.com/8.0/pythonapi/optimizer-task-gety.html}{\textit{Mosek}}, \href[pdfnewwindow]{https://www.gurobi.com/documentation/6.5/refman/farkasdual.html}{\textit{Gurobi}}, \href[pdfnewwindow]{http://www-01.ibm.com/support/docview.wss?uid=swg21400058}{\textit{CPLEX}}, \href[pdfnewwindow]{http://cvxr.com/cvx/doc/basics.html\#dual-variables}{\textit{cvxr}}/\href[pdfnewwindow]{http://cvxopt.org/userguide/coneprog.html\#linear-cone-programs}{\textit{cvxopt}}.)
    \end{itemize}
    \note[item]{It is possible to derive non-contextuality inequalities from $M$ and a known incompatible distribution $\probvec^{\mscenario}$}
    \note[item]{Note the null objective; the minimization objective is trivially always zero}
    \note[item]{The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.}
    \note[item]{If \textit{feasible}, then there exists a vector $x$ that is a valid joint distribution vector $\probvec^{\jointvar}$.}
    \note[item]{Feasibility implies that $\probvec^{\jointvar} = x$.}
    \note[item]{Infeasibility implies contextuality}
\end{frame}

\begin{frame}
    \frametitle{Known Incompatible Distribution in The Triangle Scenario}
    \cite{Fritz_2012} provides quantum-accessible distribution incompatible with TS
    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Fritz Distribution}
    The \term{Fritz Distribution $\prob[F]$}:
    \begin{itemize}
        \item three-party $\prob[F] = \prob[ABC]$
        \item each party has $4$ outcomes
    \end{itemize}
    \begin{gather*}
    \prob[F][00\textcolor{blue}{0}] = \prob[F][11\textcolor{blue}{0}] = \prob[F][30\textcolor{blue}{1}] = \prob[F][21\textcolor{blue}{1}] = \prob[F][12\textcolor{blue}{2}] = \prob[F][03\textcolor{blue}{2}] = \prob[F][23\textcolor{blue}{3}] = \prob[F][32\textcolor{blue}{3}] = \f{1}{32}\br{2 + \sqrt{2}} \\
    \prob[F][01\textcolor{blue}{0}] = \prob[F][10\textcolor{blue}{0}] = \prob[F][31\textcolor{blue}{1}] = \prob[F][20\textcolor{blue}{1}] = \prob[F][13\textcolor{blue}{2}] = \prob[F][02\textcolor{blue}{2}] = \prob[F][22\textcolor{blue}{3}] = \prob[F][33\textcolor{blue}{3}] = \f{1}{32}\br{2 - \sqrt{2}}
    \end{gather*}
    \begin{itemize}
        \item $C$'s outcome acts as measurement ``setting'' for A, B; independent of $\rho_{AB}$
        \item Correlation coarse graining $\bc{0,1,2,3} \to \bc{\br{0,3}, \br{1,2}}$
    \end{itemize}
    \[ \ba{AB | C = 0, 1, 2} = \f{1}{\sqrt{2}} \quad \ba{AB | C = 3} = - \f{1}{\sqrt{2}} \]
    \begin{itemize}
        \item Gives CHSH violation
    \end{itemize}
    \[ \ba{AB|C=0} + \ba{AB|C=1} + \ba{AB|C=2} - \ba{AB|C=3} = 2\sqrt{2} \not \leq 2 \]
\end{frame}

\begin{frame}
    \frametitle{Quantum Implementation of Fritz Distribution}
    \begin{gather*}
        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\gp^+}\bra{\gp^+} \\
        M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
        M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
    \end{gather*}
    \begin{itemize}
        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
        \item Maximally entangled Bell states:
    \end{itemize}
    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\gp^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
\end{frame}

\begin{frame}
    \frametitle{Notes of Fritz Distribution}
    \begin{itemize}
        \item Proof contingent on perfect correlation between $C$ and pseudo-settings
        \item Proof not robust to noise
    \end{itemize}
    \begin{problem}[2.17 in \cite{Fritz_2012}]
        Find an example of non-classical quantum correlations in TS together with a proof of its non-classicality which does not hinge on Bell’s Theorem.
    \end{problem}
    \begin{itemize}
        \item ``...would be helpful to have inequalities...''
        \item Possible to find inequalities violated by $\prob[F]$ using the Large inflation of the TS
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Large Inflation Incidence}
    \begin{itemize}
        \item Joint variables are all of the observable nodes $\nodes_O' = \jointvar$
        \[ \jointvar = \bc{A_1, A_2, A_3, A_4,B_1, B_2, B_3, B_4,C_1, C_2, C_3, C_4} \]
        \item Marginal scenario is composed of pre-injectable sets $\mscenario = \PreInj[\graph]{\graph'}$
        \item Inequalities Violated by Fritz distribution are inherently $4$-outcome
        \item Incidence matrix $M$ is very large $\sim 2.25 \textsf{Gb}$
        \begin{itemize}
            \item $\# \text{Columns} = 4^{12} = 16,777,216$
            \item $\# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896$
            \item $\# \text{Non-zero Entries} = 201,326,592$
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Triangle Scenario Inequality}

\section{Symmetries}
\begin{frame}
    \frametitle{Causal Symmetry}
    \begin{itemize}
        \item Desirable to find compatibility inequality $I$ such that
        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
        \item Compatibility is independent of variable labels
        \[ \forall \varphi \in \Perm{\nodes} : I \stackrel{\text{com}}{\rightarrow} \graph \implies \varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \varphi\bs{\graph}  \]
        \item If $\varphi\bs{\graph} = \graph$ then $\varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \graph$
    \end{itemize}
    \begin{definition}
        The \term{causal symmetry group} of causal structure $\graph$:
        \[ \Aut{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\bs{\graph} = \graph} \]
        Strictly speaking, one needs to preserve observable nodes:
        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Aut{\graph} \mid \varphi\bs{\nodes_O} = \nodes_O} \]
    \end{definition}
    \note<1>[item]{Fritz distribution is incompatible with Triangle scenario because party $C$ plays the role of measurement settings for both $A$ and $B$}
    \note<1>[item]{In order to find quantum distributions different from $P_F$ in the Triangle Scenario, it is therefore desirable to find a proof of its incompatibility (i.e. inequality) that is symmetric under exchange of parties}
    \note<1>[item]{Surprisingly, it is possible to do so!}
    \note<1>[item]{Here is how.}
    \note<1>[item]{First, we will formally define the symmetry group in question}
    \note<1>[item]{Causal symmetry group is the group of automorphisms on causal structure}
\end{frame}

@@

\begin{frame}[shrink=60]
    \frametitle{Party Symmetric Inequality}
    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print}
\end{frame}

@@

\begin{frame}
    \frametitle{Parameterizing Unitary Group}
    \begin{itemize}
        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} demonstrate a parameterization of $\s{U}\br{d}$ where the parameters are organized in a $d \times d$-matrix of real values $\la_{n,m}$
        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n} RP_{n,m}}} \tcdot \bs{\prod_{l=1}^{d} GP_{l}} \]
        \item Global Phase Terms: $GP_{l} = \exp\br{iP_l \lambda_{l,l}}$
        \item Relative Phase Terms: $RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$
        \item Rotation Terms: $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
        \item Projection Operators: $P_l = \ket{l}\bra{l}$
        \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
        \item Parameters $\la_{n,m} \in \bs{0, 2\pi}$
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Network Permutation Matrix}
    \begin{columns}
        \column{0.6\linewidth}
        \begin{itemize}
            \item States and measurements in the Triangle Scenario are not aligned
            \item Without $\netperm$, $\prob[ABC]$ would be separable
            \item Required to align $B$'s measurement over $\Tr_{A,C}\br{\rho_{AB} \otimes \rho_{BC}}$
            \item $\netperm$ is a $2^6 \times 2^6$ matrix
            \item Shifts one qubit to the left
        \end{itemize}
        \column{0.4\linewidth}
            \includegraphics[trim={1.0cm 1.2cm 1.0cm 1cm},clip,width=1.0\textwidth]{../../figures/perm_mtrx.pdf}
    \end{columns}
    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]

@@

\begin{frame}
    \frametitle{Conclusions}
    \begin{itemize}
        \item New causal compatibility inequalities have been found for the TS
        \item Inflation technique capable of producing inequalities with quantum/classical witnesses
        \item Proof of non-classicality is robust to noise
        \item Fritz witnessable by party symmetric inequalities
        \item Maximally violating distributions are different than Fritz but also similar
        \item Further research is necessary
    \end{itemize}
\end{frame}
